Log or not - Analysis of ECDC forecasts

### 2022-12-06 analysis/Analysis ECDC forecasts.Rmd

library(scoringutils)
library(purrr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(patchwork)
library(stringr)
library(here)
library(data.table)
library(kableExtra)
library(performance)
library(tidytext)
library(grid)
library(ggpubr)

@@

>>>>

library(scoringutils)
library(purrr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(patchwork)
library(stringr)
library(here)
library(data.table)
library(kableExtra)
library(performance)
library(tidytext)
library(grid)
library(ggpubr)
library(gh)

@@

## load anomalies (retrospecrtively revised data)
anomalies_file <- here::here("data", "anomalies.csv")
if (file.exists(anomalies_file)) {
  anomalies <- data.table::fread(file = anomalies_file)
} else {
  ## get anomalies file at date of last data made
  owner <- "covid19-forecast-hub-europe"
  repo <- "covid19-forecast-hub-europe"
  path <- "data-truth/anomalies/anomalies.csv"
  commit <- gh::gh(
    "/repos/{owner}/{repo}/commits?path={path}&until={date}",
    owner = owner,
    repo = repo,
    path = path,
    until = max(hub_data$target_end_date),
    .limit = 1
  )
  anomalies <- data.table::fread(input = URLencode(URL = paste(
    "https://raw.githubusercontent.com", owner, repo, commit[[1]]$sha, path, sep = "/"
  )))
  data.table::fwrite(x = anomalies, file = anomalies_file)
}

## prepare for mergeing into hub_data
anomalies <- anomalies[, list(
  target_end_date,
  location,
  target_type = paste0(stringr::str_to_title(stringr::str_remove(
    string = target_variable, pattern = "^inc ")), "s")
)]

hub_data <- hub_data[!anomalies, on = .(target_end_date, location, target_type)]
